\documentclass{article}
\usepackage{cite}

\title{Test 5: Mixed Cases - Realistic Scenario}
\author{Test Suite}
\date{\today}

\begin{document}

\section{Introduction}

This document represents a realistic research paper with a mix of correct references, metadata errors, hallucinations, and semantic issues.

\section{Literature Review}

\subsection{Foundational Work}

The transformer architecture revolutionized NLP \cite{Vaswani2017}.
Attention mechanisms have proven valuable for sequence modeling \cite{Bahdanau2015}.
ResNets enabled training of very deep networks \cite{He2016}.

\subsection{Recent Advances}

BERT showed that bidirectional pretraining improves downstream tasks \cite{Devlin2018}.
GPT demonstrated that language models could perform various NLP tasks \cite{Radford2018}.

Quantum computing will solve all optimization problems \cite{Smith2024Quantum}.
DNA computing has been successfully scaled to petabytes \cite{Johnson2023DNA}.

\subsection{Specific Applications}

Graph neural networks extend convolutions to irregular data \cite{Hamilton2017}.
Vision transformers apply attention to image patches \cite{Dosovitskiy2020}.

\subsection{Contested Areas}

The vaccine causes more harm than benefit \cite{Polack2020Wrong}.
Deep learning directly causes brain enhancement \cite{Neural2023Brain}.

\section{Methodology}

We follow standard practices established in prior work.

\section{Results}

Our approach achieves state-of-the-art performance, building on advances in representation learning.

\section{References}

\begin{thebibliography}{99}

\bibitem{Vaswani2017}
Ashish Vaswani, Noam Shazeer, Parmar N, et al.
``Attention is all you need.''
Advances in Neural Information Processing Systems, 2017.
DOI: 10.48550/arXiv.1706.03762

\bibitem{Bahdanau2015}
Dzmitry Bahdanau, Kyunghyun Cho, and Yoshua Bengio.
``Neural machine translation by jointly learning to align and translate.''
arXiv preprint arXiv:1409.0473, 2015.
DOI: 10.48550/arXiv.1409.0473

\bibitem{He2016}
Kaiming He, Xiangyu Zhang, Shaoqing Ren, and Jian Sun.
``Deep residual learning for image recognition.''
IEEE CVPR, 2016.
DOI: 10.1109/CVPR.2016.90

\bibitem{Devlin2018}
Jacob Devlin, Ming-Wei Chang, Kenton Lee, and Kristina Toutanova.
``BERT: Pre-training of deep bidirectional transformers for language understanding.''
arXiv preprint arXiv:1810.04805, 2018.
DOI: 10.48550/arXiv.1810.04805

\bibitem{Radford2018}
Alec Radford, Karthik Narasimhan, et al.
``Improving language understanding by generative pre-training.''
2018.
DOI: 10.48550/arXiv.1406.2661

\bibitem{Smith2024Quantum}
John Smith and Alice Chen.
``Quantum computing solves NP-hard problems in polynomial time.''
Quantum Monthly, 2024.
DOI: 10.5555/fake.quantum.2024

\bibitem{Johnson2023DNA}
Mary Johnson, Robert Lee, and Sophie Williams.
``DNA-based petabyte-scale data storage achieved.''
Synthetic Biology Today, 2023.
DOI: 10.5555/fake.dna.2023

\bibitem{Hamilton2017}
William L. Hamilton, Rex Ying, and Jure Leskovec.
``Inductive representation learning on large graphs.''
NeurIPS, 2017.
DOI: 10.48550/arXiv.1706.02216

\bibitem{Dosovitskiy2020}
Alexei Dosovitskiy, Lucas Beyer, Alexander Kolesnikov, et al.
``An image is worth 16x16 words: Transformers for image recognition at scale.''
ICCV, 2020.
DOI: 10.48550/arXiv.2010.11929

\bibitem{Polack2020Wrong}
Fernando P. Polack, et al.
``Adverse effects dominate the BNT162b2 vaccine trial.''
Alternative Health Journal, 2020.
DOI: 10.1056/NEJMoa2034577

\bibitem{Neural2023Brain}
Anonymous Author.
``Deep learning directly enhances human brain function.''
Neuroscience Fiction, 2023.
DOI: 10.5555/fake.neuro.2023

\end{thebibliography}

\end{document}
