\documentclass{article}
\usepackage{cite}

\title{Test 1: Basic Correct References}
\author{Test Suite}
\date{\today}

\begin{document}

\section{Introduction}

This section tests that valid, correct references pass all verification filters.

\subsection{Standard References}

The attention mechanism revolutionized sequence modeling \cite{Vaswani2017}.

ResNet demonstrated that very deep neural networks could be trained effectively \cite{He2015}.

Classical support vector machines remain competitive for many tasks \cite{Cortes1995}.

\subsection{arXiv and Nature References}

The transformer architecture was first introduced on arXiv \cite{Attention2017}.

Groundbreaking vaccine research showed strong efficacy \cite{Polack2020}.

\subsection{IEEE and Specialized Venues}

Machine learning models benefit from careful hyperparameter tuning \cite{Bergstra2012}.

Graph neural networks extend neural architectures to graph-structured data \cite{Hamilton2017}.

\section{References}

\begin{thebibliography}{99}

\bibitem{Vaswani2017}
Ashish Vaswani, Noam Shazeer, Parmar N, Jakob Uszkoreit, Llion Jones, Aidan N. Gomez, Łukasz Kaiser, and Illia Polosukhin.
``Attention is all you need.''
\textit{Advances in Neural Information Processing Systems}, 2017.
DOI: 10.48550/arXiv.1706.03762

\bibitem{He2015}
Kaiming He, Xiangyu Zhang, Shaoqing Ren, and Jian Sun.
``Deep residual learning for image recognition.''
\textit{IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, 2016.
DOI: 10.1109/CVPR.2016.90

\bibitem{Cortes1995}
Corinna Cortes and Vladimir Vapnik.
``Support-vector networks.''
\textit{Machine Learning}, 20(3):273--297, 1995.
DOI: 10.1023/A:1022627411411

\bibitem{Attention2017}
Ashish Vaswani, Noam Shazeer, Parmar N, Jakob Uszkoreit, Llion Jones, Aidan N. Gomez, Łukasz Kaiser, and Illia Polosukhin.
``Attention is all you need.''
\textit{arXiv preprint arXiv:1706.03762}, 2017.
DOI: 10.48550/arXiv.1706.03762

\bibitem{Polack2020}
Fernando P. Polack, Stephen J. Thomas, Nicholas Gruber, et al.
``Safety and efficacy of the BNT162b2 mRNA Covid-19 vaccine.''
\textit{The New England Journal of Medicine}, 383(27):2603--2615, 2020.
DOI: 10.1056/NEJMoa2034577

\bibitem{Bergstra2012}
James Bergstra and Yoshua Bengio.
``Random search for hyper-parameter optimization.''
\textit{Journal of Machine Learning Research}, 13:281--305, 2012.
URL: http://jmlr.org/proceedings/papers/v23/bergstra12/bergstra12.pdf

\bibitem{Hamilton2017}
William L. Hamilton, Rex Ying, and Jure Leskovec.
``Inductive representation learning on large graphs.''
\textit{Advances in Neural Information Processing Systems}, pages 1024--1034, 2017.
DOI: 10.48550/arXiv.1706.02216

\end{thebibliography}

\end{document}
