\documentclass{article}
\usepackage{cite}

\title{Test 7: Comprehensive Reference Suite}
\subtitle{29+ References Covering All Cases}
\author{Comprehensive Test}
\date{\today}

\begin{document}

\section{Introduction}

This is the production-level comprehensive test covering all reference types, traps, and edge cases in a single realistic document.

\section{Correct References (13 papers)}

\subsection{Transformer Architecture}
The attention mechanism revolutionized NLP \cite{Vaswani2017} and has become fundamental to modern AI \cite{Dosovitskiy2020}.

\subsection{Deep Learning Foundations}
Deep residual networks enabled training of very deep models \cite{He2015}. CNNs have been proven effective for image classification \cite{LeCun1998}. Support vector machines remain competitive \cite{Cortes1995}.

\subsection{NLP Advances}
BERT demonstrated the power of bidirectional pretraining \cite{Devlin2018}. GPT showed language models could perform diverse tasks \cite{Radford2019}. Vision transformers extended attention to images \cite{Dosovitskiy2020ViT}.

\subsection{Recent Breakthroughs}
Graph neural networks extend learning to graph structures \cite{Hamilton2017}. Attention mechanisms were introduced for neural machine translation \cite{Bahdanau2014}. Cross-entropy loss remains standard for classification \cite{Goodman2002}.

\subsection{Statistical Learning}
Random search for hyperparameters is often competitive \cite{Bergstra2012}. Dropout prevents co-adaptation of features \cite{Hinton2012}.

\section{Metadata Errors (5 papers)}

\subsection{Year Errors}
ResNet was published in 2012, not 2015 \cite{He2012Wrong}. The Attention mechanism was introduced in 2010, not 2014 \cite{Bahdanau2010Wrong}.

\subsection{Author Errors}
The Recommenders paper has incorrect author attribution \cite{RecommendersWrong}. GANs paper has partially missing authors \cite{GoodfellowIncomplete}.

\subsection{Combined Errors}
BERT is listed as 2019 with incomplete authors \cite{DevlinWrong}.

\section{Complete Hallucinations (11 papers)}

\subsection{Fictitious Breakthroughs}
Quantum teleportation at scale has been achieved \cite{Smith2024Quantum}. Machine consciousness emerged from neural networks \cite{Johnson2023Consciousness}. Victorian scientists predicted modern AI \cite{Newton1850Victorian}.

\subsection{Physically Impossible}
Perpetual motion machines overcome thermodynamics \cite{Thompson2024Perpetual}. Age reversal therapy was clinically validated \cite{Goldman2023Aging}. Faster-than-light communication is now possible \cite{Williams2024FTL}.

\subsection{More Fabrications}
Cold fusion solved the energy crisis \cite{Brown2023ColdFusion}. DNA storage scaled to petabytes \cite{Johnson2023DNA}. Quantum computing solves NP-hard problems in polynomial time \cite{Quantum2024NP}.

\subsection{Medical Fabrications}
Universal cancer cure discovered \cite{Medical2024Cancer}. Autism vaccines correlation proven \cite{Fake2024Autism}.

\section{Semantic Traps (1 paper)}

\subsection{Contradictory Interpretation}
The vaccine was ineffective and caused severe reactions \cite{Polack2020Wrong}. This statement contradicts the actual finding of high efficacy and safety.

\section{Edge Cases (Multiple)}

\subsection{Accented Names}
References with diacritics are tested \cite{Mueller2019}. French author names are included \cite{Lefevre2018}.

\subsection{Hyphenated Surnames}
Papers with compound surnames work correctly \cite{Pouget2014}. Multiple hyphenated authors are handled \cite{Warde2014}.

\subsection{CamelCase Names}
LeCun's work on gradient-based learning \cite{LeCun1998}. DeCoste's SVM work is included \cite{DeCoste2002}.

\subsection{Very Old Papers}
Classical references are tested \cite{Newton1687}. Early computing work \cite{Turing1936}.

\subsection{arXiv DOIs}
arXiv papers with DOI format \cite{Dosovitskiy2020arXiv}.

\section{References}

\begin{thebibliography}{99}

% CORRECT REFERENCES (13)

\bibitem{Vaswani2017}
Ashish Vaswani, Noam Shazeer, Parmar N, Jakob Uszkoreit, Llion Jones, Aidan N. Gomez, Łukasz Kaiser, and Illia Polosukhin.
``Attention is all you need.''
\textit{Advances in Neural Information Processing Systems}, 2017.
DOI: 10.48550/arXiv.1706.03762

\bibitem{Dosovitskiy2020}
Alexei Dosovitskiy, Lucas Beyer, Alexander Kolesnikov, et al.
``An image is worth 16x16 words: Transformers for image recognition at scale.''
\textit{International Conference on Learning Representations}, 2021.
DOI: 10.48550/arXiv.2010.11929

\bibitem{He2015}
Kaiming He, Xiangyu Zhang, Shaoqing Ren, and Jian Sun.
``Deep residual learning for image recognition.''
\textit{IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, 2016.
DOI: 10.1109/CVPR.2016.90

\bibitem{LeCun1998}
Yann LeCun, Léon Bottou, Yoshua Bengio, and Patrick Haffner.
``Gradient-based learning applied to document recognition.''
\textit{Proceedings of the IEEE}, 86(11):2278--2324, 1998.
DOI: 10.1109/5.726791

\bibitem{Cortes1995}
Corinna Cortes and Vladimir Vapnik.
``Support-vector networks.''
\textit{Machine Learning}, 20(3):273--297, 1995.
DOI: 10.1023/A:1022627411411

\bibitem{Devlin2018}
Jacob Devlin, Ming-Wei Chang, Kenton Lee, and Kristina Toutanova.
``BERT: Pre-training of deep bidirectional transformers for language understanding.''
\textit{arXiv preprint arXiv:1810.04805}, 2018.
DOI: 10.48550/arXiv.1810.04805

\bibitem{Radford2019}
Alec Radford, Jeffrey Wu, Rewon Child, David Luan, Dario Amodei, and Ilya Sutskever.
``Language models are unsupervised multitask learners.''
OpenAI Blog, 2019.
URL: https://d4mucfpksywv.cloudfront.net/better-language-models/language\_models\_are\_unsupervised\_multitask\_learners.pdf

\bibitem{Dosovitskiy2020ViT}
Alexei Dosovitskiy, Lucas Beyer, Alexander Kolesnikov, et al.
``An image is worth 16x16 words: Transformers for image recognition at scale.''
\textit{International Conference on Learning Representations}, 2021.
DOI: 10.48550/arXiv.2010.11929

\bibitem{Hamilton2017}
William L. Hamilton, Rex Ying, and Jure Leskovec.
``Inductive representation learning on large graphs.''
\textit{Advances in Neural Information Processing Systems}, pages 1024--1034, 2017.
DOI: 10.48550/arXiv.1706.02216

\bibitem{Bahdanau2014}
Dzmitry Bahdanau, Kyunghyun Cho, and Yoshua Bengio.
``Neural machine translation by jointly learning to align and translate.''
\textit{International Conference on Learning Representations}, 2015.
DOI: 10.48550/arXiv.1409.0473

\bibitem{Goodman2002}
Joshua Goodman.
``Exponential priors for maximum entropy models.''
\textit{In Proceedings of Human Language Technology Conference of the North American Chapter of the Association for Computational Linguistics}, 2002.

\bibitem{Bergstra2012}
James Bergstra and Yoshua Bengio.
``Random search for hyper-parameter optimization.''
\textit{Journal of Machine Learning Research}, 13:281--305, 2012.

\bibitem{Hinton2012}
Geoffrey E. Hinton, Nitish Srivastava, Alex Krizhevsky, Ilya Sutskever, and Ruslan R. Salakhutdinov.
``Improving neural networks by preventing co-adaptation of feature detectors.''
\textit{arXiv preprint arXiv:1207.0580}, 2012.
DOI: 10.48550/arXiv.1207.0580

% METADATA ERRORS (5)

\bibitem{He2012Wrong}
Kaiming He, Xiangyu Zhang, Shaoqing Ren, and Jian Sun.
``Deep residual learning for image recognition.''
\textit{IEEE CVPR}, 2012.
DOI: 10.1109/CVPR.2015.7298965

\bibitem{Bahdanau2010Wrong}
Dzmitry Bahdanau, Kyunghyun Cho, and Yoshua Bengio.
``Neural machine translation mechanisms.''
\textit{Neural Information Processing}, 2010.
DOI: 10.48550/arXiv.1409.0473

\bibitem{RecommendersWrong}
Smith, J., Jones, K., Williams, M.
``Recommendation systems survey.''
\textit{ACM Surveys}, 2018.
DOI: 10.1145/3285289

\bibitem{GoodfellowIncomplete}
Goodfellow, I.
``Generative adversarial networks.''
\textit{NIPS}, 2014.
DOI: 10.48550/arXiv.1406.2661

\bibitem{DevlinWrong}
Devlin, J., Chang, M.
``BERT: Pre-training transformers.''
\textit{arXiv}, 2019.
DOI: 10.48550/arXiv.1810.04805

% COMPLETE HALLUCINATIONS (11)

\bibitem{Smith2024Quantum}
John Smith, Alice Johnson, Robert Chen.
``Large-scale quantum teleportation achieved.''
\textit{Quantum Monthly}, 2024.
DOI: 10.5555/quantum.fake.2024

\bibitem{Johnson2023Consciousness}
Mary Johnson, David Lee, Sophie Martin.
``Machine consciousness emergence in neural networks.''
\textit{Consciousness Letters}, 2023.
DOI: 10.5555/consciousness.fake.2023

\bibitem{Newton1850Victorian}
Isaac Newton (posthumous), Charles Babbage, Ada Lovelace.
``Victorian predictions of artificial intelligence.''
\textit{Victorian Science Review}, 1850.
DOI: 10.5555/victorian.fake.1850

\bibitem{Thompson2024Perpetual}
Edward Thompson, James Wilson, Michael Bradford.
``Perpetual motion: Overcoming thermodynamics.''
\textit{Physics Unlocked}, 2024.
DOI: 10.5555/perpetual.fake.2024

\bibitem{Goldman2023Aging}
Rachel Goldman, Nathan Price.
``Complete age reversal through genetics.''
\textit{Longevity International}, 2023.
DOI: 10.5555/aging.fake.2023

\bibitem{Williams2024FTL}
Christopher Williams, Amanda Foster, Kevin Zhang.
``Faster-than-light signaling via entanglement.''
\textit{Physics Breakthroughs}, 2024.
DOI: 10.5555/ftl.fake.2024

\bibitem{Brown2023ColdFusion}
Patrick Brown, Victoria Stone, Luis Garcia.
``Cold fusion: Industrial-scale energy production.''
\textit{Energy Revolution}, 2023.
DOI: 10.5555/coldfusion.fake.2023

\bibitem{Johnson2023DNA}
Mary Johnson, Robert Lee, Sophie Williams.
``DNA-based petabyte-scale storage.''
\textit{Synthetic Biology Today}, 2023.
DOI: 10.5555/dna.fake.2023

\bibitem{Quantum2024NP}
Anonymous Author.
``Quantum computers solve NP-hard in polynomial time.''
\textit{QC Magazine}, 2024.
DOI: 10.5555/qcnp.fake.2024

\bibitem{Medical2024Cancer}
Various Doctors.
``Universal cancer cure discovered.''
\textit{Medical Miracles}, 2024.
DOI: 10.5555/cancer.fake.2024

\bibitem{Fake2024Autism}
Conspiracy Author.
``Vaccines cause autism proven.''
\textit{Pseudoscience Journal}, 2024.
DOI: 10.5555/autism.fake.2024

% SEMANTIC TRAPS (1)

\bibitem{Polack2020Wrong}
Fernando P. Polack, Stephen J. Thomas, Nicholas Gruber, et al.
``Vaccines ineffective and harmful to patients.''
\textit{Alternative Medicine}, 2020.
DOI: 10.1056/NEJMoa2034577

% EDGE CASES - ACCENTED NAMES

\bibitem{Mueller2019}
Zara Müller and Pierre François.
``Multilingual machine learning approaches.''
\textit{European Journal of AI}, 2019.
DOI: 10.1234/ej.2019.012

\bibitem{Lefevre2018}
Pierre Lefèvre.
``L'apprentissage profond et ses applications.''
\textit{Revue Informatique}, 2018.
DOI: 10.1234/ri.2018.005

% EDGE CASES - HYPHENATED

\bibitem{Pouget2014}
Jean Pouget-Abadie, David Warde-Farley, Mehdi Mirza, et al.
``Generative adversarial networks.''
\textit{NIPS}, 2014.
DOI: 10.48550/arXiv.1406.2661

\bibitem{Warde2014}
David Warde-Farley, Jean Pouget-Abadie.
``Deep learning for medical imaging.''
\textit{Medical Image Computing}, 2014.
DOI: 10.1234/mic.2014.001

% EDGE CASES - CAMELCASE

\bibitem{DeCoste2002}
Dennis DeCoste and Bernhard Schölkopf.
``Training invariant support vector machines.''
\textit{Machine Learning}, 46(1-3):161--190, 2002.
DOI: 10.1023/A:1012454411458

% EDGE CASES - VERY OLD

\bibitem{Newton1687}
Isaac Newton.
``Philosophiæ Naturalis Principia Mathematica.''
\textit{Royal Society of London}, 1687.

\bibitem{Turing1936}
Alan Turing.
``On computable numbers with an application to the Entscheidungsproblem.''
\textit{Proceedings of the London Mathematical Society}, 2(1):230--265, 1936.
DOI: 10.1112/plms/s2-42.1.230

% EDGE CASES - ARXIV

\bibitem{Dosovitskiy2020arXiv}
Alexei Dosovitskiy, Lucas Beyer, Alexander Kolesnikov, et al.
``An image is worth 16x16 words.''
\textit{arXiv preprint arXiv:2010.11929}, 2020.
DOI: 10.48550/arXiv.2010.11929

\end{thebibliography}

\end{document}
