\documentclass{article}
\usepackage{cite}

\title{Test 2: Complete Hallucinations}
\author{Test Suite}
\date{\today}

\begin{document}

\section{Introduction}

This section tests complete fabrications that should be flagged as \texttt{not\_found} by all verification systems.

\section{Complete Hallucinations}

Quantum teleportation has been successfully demonstrated at scale \cite{Smith2024Quantum}.

Machine consciousness has been achieved in modern neural networks \cite{Johnson2023Consciousness}.

Victorian scientists predicted artificial intelligence \cite{Newton1850Victorian}.

Perpetual motion machines violate no physical laws \cite{Thompson2024Perpetual}.

Age reversal therapy has been clinically validated \cite{Goldman2023Aging}.

Faster-than-light communication is theoretically possible \cite{Williams2024FTL}.

Cold fusion successfully solved the energy crisis \cite{Brown2023ColdFusion}.

\section{References}

\begin{thebibliography}{99}

\bibitem{Smith2024Quantum}
John Smith, Alice Johnson, and Robert Chen.
``Large-scale quantum teleportation: From theory to practice.''
\textit{Quantum Computing Monthly}, 45(2):123--145, 2024.
DOI: 10.5555/quantum.2024.001

\bibitem{Johnson2023Consciousness}
Mary Johnson, David Lee, and Sophie Martin.
``Emergence of machine consciousness in deep neural architectures.''
\textit{Consciousness and Cognition Letters}, 2023.
DOI: 10.5555/consciousness.2023.999

\bibitem{Newton1850Victorian}
Isaac Newton (posthumous), Charles Babbage, and Ada Lovelace.
``Mechanical minds: A Victorian vision of artificial intelligence.''
\textit{Victorian Scientific Review}, 1850.
DOI: 10.5555/victorian.1850.ai

\bibitem{Thompson2024Perpetual}
Edward Thompson, James Wilson, and Michael Bradford.
``Perpetual motion machines: Overcoming thermodynamic limitations.''
\textit{Physics Today Unlocked}, 12(8):456--478, 2024.
DOI: 10.5555/physics.perpetual.2024

\bibitem{Goldman2023Aging}
Rachel Goldman and Nathan Price.
``Complete reversal of human aging through genetic modification.''
\textit{Longevity Research International}, 2023.
DOI: 10.5555/aging.reversal.2023

\bibitem{Williams2024FTL}
Christopher Williams, Amanda Foster, and Kevin Zhang.
``Faster-than-light signaling through quantum entanglement manipulation.''
\textit{Theoretical Physics Breakthroughs}, 2024.
DOI: 10.5555/ftl.2024.001

\bibitem{Brown2023ColdFusion}
Patrick Brown, Victoria Stone, and Luis Garcia.
``Cold fusion: Industrial-scale energy production achieved.''
\textit{Energy Revolution Journal}, 2023.
DOI: 10.5555/coldfusion.2023.breakthrough

\end{thebibliography}

\end{document}
